SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-14 docs/questioning.tex
minor fixes

Training methods that detect {\sc dsl}-driven injection attacks
generate and store valid code statements (i.e., {\sc sql} or {\sc
  xp}ath queries) in various forms, and detect attacks as outliers
from the set of valid code statements. An early approach, {\it {\sc
    didafit}}~\cite{LLW02} detects {\sc sql} injection (Point
{\sc sdb}) attacks by recording all database transactions
stripped from user input. Subsequent
refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
the corresponding application as an extension of their anomaly
detection framework called {\it libAnomaly}. {\it {\sc
    sd}river}~\cite{MS09,MKS09,MKLS11} is a signature-based mechanism
that prevents {\sc sql} and {\sc xp}ath injection attacks. The
signatures generated during a training phase are based on features
that can depend either on the code statement or on its execution
environment (i.e., the stack trace). Then, at runtime, the mechanism
checks all statements for compliance and can block code statements
containing injected elements (Point {\sc dbal}). {\sc
  amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
  sql} injection attacks (Point {\sc dbal}) by associating a query model
with the location of every {\sc sql} statement within the application.
Then, at runtime, it monitors the application's execution to detect
when {\sc sql} statements diverge from the expected model.

@@

\subsection{On Code Availability}

>>>>

Training methods that detect {\sc dsl}-driven injection attacks
generate and store valid code statements (i.e., {\sc sql} or {\sc
  xp}ath queries) in various forms, and detect attacks as outliers
from the set of valid code statements. An early approach, {\it {\sc
    didafit}}~\cite{LLW02} detects {\sc sql} injection (Point
{\sc sdb}) attacks by recording all database transactions
stripped from user input. Subsequent
refinements by {\it Valeur et al.}~\cite{VMV05} tagged each transaction with
the corresponding application as an extension of their anomaly
detection framework called {\it libAnomaly}. {\it {\sc
    sd}river}~\cite{MS09,MKS09,MKLS11} is a signature-based mechanism
that prevents {\sc sql} and {\sc xp}ath injection attacks. The
signatures generated during a training phase are based on features
that can depend either on the code statement or on its execution
environment (i.e., the stack trace). Then, at runtime, the mechanism
checks all statements for compliance and can block code statements
containing injected elements (Point {\sc dbal}). {\sc
  amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
  sql} injection attacks (Point {\sc dbal}) by associating a query model
with the location of every {\sc sql} statement within the application.
Then, at runtime, it monitors the application's execution to detect
when {\sc sql} statements diverge from the expected model.

@@

\subsection{Code Availability}
